Power simulations

### 2022-12-10 Power.Rmd
Update Power.Rmd

summary(power_models$BIO_CDA.PhasicMax1)
sim_SCR <- powerSim(power_models$BIO_CDA.PhasicMax1,test = fixed("arousal_c:valence_c", "z"),
                    nsim = 100)

@@

 pc_scr100<- powerCurve(extendedscr100, along="ssid", nsim = 100)
 plot(pc_scr100)

@@

# extendedscr100_int@call
pc_scr100_int<- powerCurve(extendedscr1002,
                           test = fixed("arousal_c:valence_c", "z"),
                           along="ssid", nsim = 50)

>>>>

summary(power_models$BIO_CDA.PhasicMax1)
sim_SCR <- powerSim(power_models$BIO_CDA.PhasicMax1,
                    nsim = 100)

@@

# pc_scr100<- powerCurve(extendedscr100, along="ssid", nsim = 100)
 # plot(pc_scr100)

@@

# extendedscr100_int@call
pc_scr100_int<- powerCurve(extendedscr1002,
                           test = fixed("valence_c", "z"),
                           along="ssid", nsim = 50)
